---
title: "Figures and Tables"
format:
  html:
    fig-dpi: 350
    toc: true
    toc-title: Contents
    toc-depth: 2
    fig-pos: 'h'
    fig-align: center
    fig-cap-location: top
    tbl-cap-location: top
execute:
  echo: false
  warning: false
  message: false
---

# Primary analysis

```{r}
#| label: setup
#| include: false

# Load packages
library(readxl)
library(tidyverse)
library(gtsummary)
library(gt)
library(survival)
library(survminer)
library(ggsurvfit)
library(consort)
library(tidycmprsk)
library(mice)
library(randomForest)
library(boot)
library(rlist)
library(grid)
library(gridExtra)
library(forcats)

# Import data
df <- read_excel("Data/cohort.xlsx")

# Create function to report point estimate and 95% CI
report_result <- function(point, conf.low, conf.high) {
  return(paste0(format(round(point, 2), nsmall = 2),
                " (", format(round(conf.low, 2), nsmall = 2), ", ",
                format(round(conf.high, 2), nsmall = 2), ")"))
}

# Create function to report point estimate only
report_point_est <- function(point) {
  return(format(round(point, 2), nsmall = 2))
}

# Create function to report 95% CI only
report_conf_int <- function(conf.low, conf.high) {
  return(paste0(format(round(conf.low, 2), nsmall = 2),
                ", ",
                format(round(conf.high, 2), nsmall = 2)))
}
```

## Figure 1. Consort diagram

```{r}
#| label: fig-consort
#| fig-cap: Consort diagram

# Labels
labels <- c(
  "Enrolled in the JHHCC and attended\n≥1 HIV primary care visit between\n01 January 2012 and 31 December 2024 (n=", # Top-of-the-funnel
  # "Excluded (n=", # Total exclusion
  # "\u2022 Died on or before 01-Jan-2012 (n=", # First exclusion
  "\u2022 Not diagnosed with OUD on or after 01 January 2012 (n=", # Second exclusion
  # "\u2022 Did not visit the clinic in the past 12 months (n=", # Third exclusion
  "Included in descriptive analysis (n=", # Study population
  "\u2022 No nonprescribed opioid use in the past year (n=",
  "\u2022 Receiving MOUD treatment at study entry (n=",
  "Included in time-to-MOUD initiation analysis (n="
  )

# Counts
counts <- c(
  nrow(df), # Top-of-the-funnel
  # nrow(df %>% filter(if_any(starts_with("incl_"), ~ .x == 0))), # Total exclusion
  # nrow(df %>% filter(incl_entry == 0)), # First exclusion
  nrow(df %>% filter(incl_entry == 0 | incl_dx_oud == 0)), # Second exclusion
  # nrow(df %>% filter(incl_entry + incl_dx_oud == 2 & incl_pastyr == 0)), # Third exclusion
  nrow(df %>% filter(if_all(starts_with("incl_"), ~ .x == 1))), # Study population
  nrow(df %>% filter(if_all(starts_with("incl_"), ~ .x == 1) & (base_int_oud == 0 | is.na(base_int_oud)))),
    nrow(df %>% filter(if_all(starts_with("incl_"), ~ .x == 1) & base_int_oud == 1 & active_med_bup + active_med_mthd >= 1)), # Active med exclusion
  nrow(df %>% filter(if_all(starts_with("incl_"), ~ .x == 1) & base_int_oud == 1 & active_med_bup == 0 & active_med_mthd == 0)) # TTI analysis population
  )

# Specify the diagram
txt1 <- paste0(labels[1], counts[1], ")")
txt1_side <- paste0(
  labels[2], counts[2], ")"
  # labels[3], counts[3], ")\n",
  # labels[4], counts[4], ")"
  # labels[5], counts[5], ")"
  )
txt2 <- paste0(labels[3], counts[3], ")")
txt2_side <- paste0(
  labels[4], counts[4], ")\n",
  labels[5], counts[5], ")"
                    )
txt3 <- paste0(labels[6], counts[6], ")")

# Display diagram
consort_plot <- add_box(txt = txt1) %>%
  add_side_box(txt = txt1_side) %>%
  add_box(txt = txt2) %>%
  add_side_box(txt = txt2_side) %>%
  add_box(txt = txt3)
```
Note: 01-Jan-2012 was approximately the date when people with HIV (PWH) were universally treated with HAART instead of waiting for their CD4 counts to fall below a value.
\newpage

## Table 1. Baseline characteristics

```{r}
#| label: tbl-base
#| tbl-cap: Baseline characteristics

# Obtain analytic cohort
analytic_cohort <- df %>% filter(analytic_cohort == 1) %>%
  mutate(
    new_by_group = case_when(
    incl_dx_oud + base_int_oud == 2 & group %in% c("Buprenorphine", "Methadone") ~ "Prevalent MOUD",
    incl_dx_oud + base_int_oud == 2 & group == "No treatment" ~ "No MOUD, ongoing opioid use",
    TRUE ~ "No ongoing opioid use"
    ),
    new_by_group = factor(new_by_group, levels = c("No ongoing opioid use", "Prevalent MOUD", "No MOUD, ongoing opioid use"))
  )

# Display table
analytic_cohort %>%
  select(new_by_group, age, birthmale, black, msm, idu, starts_with("base_"), index_su_mh, base_svc_psych, index_year) %>%
  tbl_summary(
    by = new_by_group,
    label = c(
      age ~ "Age", birthmale ~ "Male sex", black ~ "Black race",
      msm ~ "History of MSM", idu ~ "History of IDU",
      base_dx_depr ~ "Depression", base_dx_anxi ~ "Anxiety",
      base_dx_bipo ~ "Bipolar disorder", base_dx_schi ~ "Schizophrenia",
      base_dx_ptsd ~ "PTSD", base_dx_aud ~ "Alcohol use disorder",
      base_dx_cud ~ "Cocaine use disorder", base_int_oud ~ "Non-prescribed opioids",
      base_int_cud ~ "Cocaine", base_int_hazalc = "Unhealthy alcohol",
      base_int_mud ~ "Cannabis",
      base_med_bup ~ "Buprenorphine", base_med_mthd ~ "Methadone",
      # base_svc_use ~ "Visited primary care",
      base_svc_appt ~ "Number of visits scheduled",
      base_svc_prop ~ "Proportion of visits completed",
      base_svc_psych ~ "Mental health service use",
      index_su_mh ~ "Substance use or mental health",
      index_year ~ "Year"
      ),
    # type = list(svc_use ~ "continuous2"),
    statistic = list(
      base_svc_prop ~ "{mean} ({sd})"
      # svc_use ~ c("{N_nonmiss}", "{sum}", "{mean} ({sd})")
      ),
    digits = list(
      index_year ~ purrr::partial(style_number, digits = 0, big.mark = ""),
      all_categorical() ~ c(0, 1)
      )
    ) %>%
  modify_table_body(
    mutate,
    groupname_col = case_when(
      variable %in% c("age", "birthmale", "black") ~ "Patient demographics",
      variable %in% c("msm", "idu") ~ "HIV acquisition factors",
      variable %in% colnames(df)[grepl("base_dx_", colnames(df))] ~ "Diagnoses",
      variable %in% colnames(df)[grepl("base_int_", colnames(df))] ~ "Recent drug use",
      variable %in% colnames(df)[grepl("base_med_", colnames(df))] ~ "History of MOUD",
      variable %in% colnames(df)[grepl("base_svc_", colnames(df))] ~ "Healthcare service utilization",
      variable %in% c("index_su_mh", "index_year") ~ "Index diagnosis"
    )
  ) %>%
  modify_column_indent(label, rows = row_type == "label", indent = 4L) %>%
  modify_column_indent(label, rows = row_type %in% c("level", "missing"), indent = 8L) %>%
  add_overall(last = TRUE) %>%
  # modify_spanning_header(c("stat_1", "stat_2") ~ "**Active use**") %>%
  remove_row_type(variables = c(base_svc_appt, base_svc_prop), type = "missing") %>%
  as_gt() %>%
  opt_vertical_padding(scale = 0.25)
  # tab_footnote(
  #   footnote = "Human immunodeficiency virus",
  #   locations = cells_row_groups(groups = starts_with("HIV"))
  #   ) %>%
  # tab_footnote(
  #   footnote = "Men who have sex with men",
  #   locations = cells_body(
  #     columns = label,
  #     rows = label == "History of MSM"
  #     )
  #   ) %>%
  # tab_footnote(
  #   footnote = "Injection drug use",
  #   locations = cells_body(
  #     columns = label,
  #     rows = label == "History of IDU"
  #     )
  #   ) %>%
  # tab_footnote(
  #   footnote = "Post-traumatic stress disorder",
  #   locations = cells_body(
  #     columns = label,
  #     rows = label == "PTSD"
  #     )
  #   )
```
@tbl-base shows the baseline characteristics of the study population.
\newpage

## Figure 2. Cumulative incidence functions

```{r}
#| label: fig-tte
#| fig-cap: Time from index OUD diagnosis to the earliest of 1) buprenorphine initiation, 2) methadone initiation, 3) opioid free in past year, 4) Loss to clinical follow up, and 5) death

# Obtain primary survival cohort
survival_cohort <- df %>%
  filter(survival_cohort == 1) %>%
  mutate(
    time_years = time / 365.25,
    time_months = time / 30.417
    )

# Option to change line colors
options("ggsurvfit.switch-color-linetype" = TRUE)

# Display CIFs
cif <- tidycmprsk::cuminc(Surv(time_years, factor(event)) ~ 1,
                          survival_cohort) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5"), linewidth = 0.8) +
  labs(
    x = "Years since index OUD diagnosis",
    y = "Cumulative incidence"
    ) +
  theme_survminer() +
  scale_ggsurvfit(x_scales = list(limits = c(0, 5.1))) +
  theme(
    axis.line = element_line(colour = "#6a6868"),
    axis.ticks = element_line(colour = "#6a6868"),
    panel.grid.major.y = element_line(colour = "#d1ced0")
    # axis.text.y = element_text(size = 12),
    # axis.text.x = element_text(size = 12),
    # axis.title.y = element_text(size = 16),
    # axis.title.x = element_text(size = 16),
    # legend.text = element_text(size = 12)
    ) +
  add_risktable(
    risktable_stats = "n.risk",
    stats_label = "No. at risk",
    size = 4.2,
    theme = theme_risktable_default(axis.text.y.size = 12)
    ) +
  scale_color_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  scale_fill_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  guides(color = guide_legend(nrow = 2))

# Import a function to create desired data frame
source("competing_risk_df_2.R")

cif$data <- competing_risk_df_2(
  df_in = cif$data,
  order = c("1", "2", "5", "4", "3")
  )

# competing_events <- cif$data %>%
#   filter(outcome == "2") %>%
#   slice_max(time) %>%
#   pull(estimate)
# 
# primary_event <- cif$data %>%
#   filter(outcome == "1") %>%
#   slice_max(time) %>%
#   pull(estimate)

cif + theme(
  axis.title = element_text(size = 50)
  )

ggsave("cif.png", plot = plot(cif), width = 1050, height = 600, units = "px")
ggsave("cif.png", plot = plot(cif), width = 1210, height = 720, units = "px")
```
@fig-tte shows the cumulative incidence functions for each competing event.
\newpage

## Table 2. Survival results

```{r}
#| label: bootstrap-cif

# Set seed for reproducibility
set.seed(1110)

cif_boot <- function(df, indices) {
  
  df_sample <- df[indices, ]
  
  cif_sample <- (tidycmprsk::cuminc(Surv(time_years, factor(event)) ~ 1,
                                    df_sample) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5")))$data
  
  # Calculate CI at 1, 2, and 5 years
  cif_calc <- list()
  
  cif_calc$year_1 <- cif_sample %>%
    group_by(outcome) %>%
    filter(time <= 5) %>%
    {. ->> cif_calc$year_5} %>%
    filter(time <= 2) %>%
    {. ->> cif_calc$year_2} %>%
    filter(time <= 1)
  
  result <- c()
  
  for (i in 1:length(cif_calc)) {
    
    result[i] <- cif_calc[[i]] %>%
      slice_max(time) %>%
      ungroup() %>%
      summarize(1 - sum(estimate)) %>%
      pull()
    
  }
  
  return(result)
  
}

# Get bootstrap results
cif_result <- boot(survival_cohort, cif_boot, 500)

# Report point estimates
eligible_point <- report_point_est(summary(cif_result)[, 2]) %>% rev()

# Report confidence intervals
eligible_conf <- report_conf_int(summary(cif_result)[, 2] - qnorm(0.975) * summary(cif_result)[, 4],
                summary(cif_result)[, 2] + qnorm(0.975) * summary(cif_result)[, 4]) %>% rev()

# Get probabilities for all events
cif_df <- (tidycmprsk::cuminc(Surv(time_years, factor(event)) ~ 1,
                                    survival_cohort) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5")))$data

cif_calc <- list()

cif_calc$year_1 <- cif_df %>%
    group_by(outcome) %>%
    filter(time <= 5) %>%
    {. ->> cif_calc$year_5} %>%
    filter(time <= 2) %>%
    {. ->> cif_calc$year_2} %>%
    filter(time <= 1)

cif_calc <- list.reverse(cif_calc)

result <- list()
  
for (i in 1:length(cif_calc)) {
    
  result[[i]] <- cif_calc[[i]] %>%
    slice_max(time) %>%
    ungroup() %>%
    mutate(
      point = report_point_est(estimate),
      conf = report_conf_int(conf.low, conf.high)
      ) %>%
    select(point, conf)
  
}

cif_report_1 <- list.cbind(result) %>%
  rbind(c(rbind(eligible_point, eligible_conf)))

names(cif_report_1) <- c("1_year_point", "1_year_conf",
                         "2_year_point", "2_year_conf",
                         "5_year_point", "5_year_conf")

event <- c("Buprenorphine initiation", "Methadone initiation",
           "Sustained remission", "Loss to clinical follow up",
           "Death", "Remaining eligible")

event %>%
  cbind(cif_report_1) %>%
  rename(Event = ".") %>%
  gt() %>%
  cols_label(
    "1_year_point" = "Probability",
    "1_year_conf" = "95% CI",
    "2_year_point" = "Probability",
    "2_year_conf" = "95% CI", 
    "5_year_point" = "Probability",
    "5_year_conf" = "95% CI"
    ) %>%
  tab_spanner(label = "1 Year",
              columns = c("1_year_point", "1_year_conf")) %>%
  tab_spanner(label = "2 Years",
              columns = c("2_year_point", "2_year_conf")) %>%
  tab_spanner(label = "5 Years",
              columns = c("5_year_point", "5_year_conf")) %>%
  opt_vertical_padding(scale = 0.25) %>%
  tab_footnote(
    footnote = "Confidence interval",
    locations = cells_column_labels(columns = ends_with("conf"))
    )

# Get unrounded 1-year, 2-year, and 5-year probabilities of buprenorphine initiation for dot plot
unrounded_result <- list()

for (i in 1:length(cif_calc)) {
    
  unrounded_result[[i]] <- cif_calc[[i]] %>%
    slice_max(time) %>%
    ungroup() %>%
    mutate(
      point = estimate,
      conf = paste(conf.low, conf.high, sep = ", ")
      ) %>%
    select(point, conf)
  
}

unrounded_cif_report_1 <- list.cbind(unrounded_result)[1, ]

names(unrounded_cif_report_1) <- c("1_year_point", "1_year_conf",
                         "2_year_point", "2_year_conf",
                         "5_year_point", "5_year_conf")
```

```{r}
#| label: tbl-results
#| tbl-cap: Restricted mean time lost (RMTL) for each competing event

# Get CIF data from the function
cum_inc <- tidycmprsk::cuminc(Surv(time_months, factor(event)) ~ 1,
                          survival_cohort) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5"))

# Calculate RMTL
cif_data <- cum_inc$data %>%
  group_by(outcome) %>%
  mutate(
    time_diff = lead(time) - time,
    auc = estimate * time_diff,
    rmtl = cumsum(auc),
    var = (cum.event / (cum.event - 1)) * cumsum(n.event * (max(rmtl, na.rm = T) - rmtl)^2 / (n.risk * (n.risk - n.event))),
    rmtl.std.error = sqrt(var),
    rmtl.conf.high = rmtl + qnorm(0.975) * rmtl.std.error,
    rmtl.conf.low = rmtl - qnorm(0.975) * rmtl.std.error
    ) %>%
  ungroup()

# Report RMTL for tau = max
cif_data %>%
  group_by(outcome) %>%
  filter(row_number() == n() - 1) %>%
  ungroup() %>%
  mutate(
    Event = case_when(
      outcome == "1" ~ "Buprenorphine initiation",
      outcome == "2" ~ "Methadone initiation",
      outcome == "3" ~ "Sustained remission",
      outcome == "4" ~ "Loss to clinical follow up",
      outcome == "5" ~ "Death",
      TRUE ~ NA_character_
    ),
    rmtl = report_point_est(rmtl),
    conf = report_conf_int(rmtl.conf.low, rmtl.conf.high)
    ) %>%
  select(Event, rmtl, conf) %>%
  gt() %>%
  cols_label(
    rmtl = "RMTL",
    conf = "95% CI"
    ) %>%
  opt_vertical_padding(scale = 0.25) %>%
  tab_footnote(
    footnote = "Restricted mean time lost, in months",
    locations = cells_column_labels(columns = rmtl)
    ) %>%
  tab_footnote(
    footnote = "Confidence interval",
    locations = cells_column_labels(columns = conf)
    )
```

```{r}
#| label: fig-missing
#| fig-cap: Missing data patterns
#| include: false

# Select variables to be used in the model
survival_cohort_impute_prep <- survival_cohort %>%
  transmute(
    age_5yr = (age - 50) / 5, birthmale, black, year_2019,
    base_dx_anxi, base_dx_bipo, base_dx_depr,
    base_dx_aud, base_dx_cud,
    base_int_hazalc, base_int_cud, base_int_mud,
    base_med_bup, base_med_mthd,
    base_svc_appt, base_svc_psych, time, event
    )

# Change binary variables to factor in preparation for imputation
survival_cohort_impute_prep[, -c(1, 15, 17)] <- lapply(survival_cohort_impute_prep[, -c(1, 15, 17)], as.factor)

# Plot data missingness patterns
# md.pattern(
#   survival_cohort_impute_prep,
#   rotate.names = TRUE
#   )
```

```{r}
#| include: false
#| label: run-imputations

# Set seed for reproducibility
set.seed(1110)

# Number of data sets to impute
K <- 40

# Impute data sets
survival_imputed <- replicate(
  n = K,
  rfImpute(event ~ ., survival_cohort_impute_prep),
  simplify = FALSE
  )
```

## Table 3. Model results

```{r}
#| label: tbl-model-results
#| tbl-cap: Subdistribution hazard ratios and 95% confidence intervals for each covariate for all four competing events

# Create matrix to store results
# '@ncol indicates number of outcomes
# '@nrow indiciates number of predictors
pooled_results <- matrix(, nrow = 16, ncol = 5)

# Perform for all 5 competing events
for (i in 1:5) {
  
  # Specify the model
  formula <- as.formula(
    paste("Surv(time, factor(event == ", i, ")) ~ ",
    paste(colnames(survival_cohort_impute_prep)[c(1:16)], collapse = " + "))
    )
  
  # Fit model over all imputed data sets
  fit <- lapply(survival_imputed, function(x) tidycmprsk::crr(formula, x))
  
  # Pool model results
  pooled_fit <- summary(pool(fit))
  
  # Point estimate and SE
  point <- exp(pooled_fit$estimate)
  conf.low <- exp(pooled_fit$estimate - qnorm(0.975) * pooled_fit$std.error)
  conf.high <- exp(pooled_fit$estimate + qnorm(0.975) * pooled_fit$std.error)
  
  # Output results
  pooled_results[, i] <- t(report_result(point, conf.low, conf.high))
}

# Label covariates
covariate_labels <- c(
  "Age, 5-yrs",
  "Male sex",
  "Black race",
  "Index year ≥2019",
  "Anxiety",
  "Bipolar disorder",
  "Depression",
  "Alcohol use disorder",
  "Cocaine use disorder",
  "Recent heavy alcohol use",
  "Recent cocaine use",
  "Recent cannabis use",
  "History of buprenorphine",
  "History of methadone",
  "No. of primary care appointments",
  "Use of mental health services"
)

# Output results
covariate_labels %>%
  cbind(as.data.frame(pooled_results)) %>%
  rename(Predictor = ".") %>%
  separate(V1, c("bup_hr", "bup_ci"), sep = " ", extra = "merge") %>%
  separate(V2, c("mthd_hr", "mthd_ci"), sep = " ", extra = "merge") %>%
  separate(V3, c("of1_hr", "of1_ci"), sep = " ", extra = "merge") %>%
  separate(V4, c("ltc_hr", "ltc_ci"), sep = " ", extra = "merge") %>%
  separate(V5, c("dth_hr", "dth_ci"), sep = " ", extra = "merge") %>%
  mutate(
    bup_ci = gsub("[()]", "", bup_ci),
    mthd_ci = gsub("[()]", "", mthd_ci),
    of1_ci = gsub("[()]", "", of1_ci),
    ltc_ci = gsub("[()]", "", ltc_ci),
    dth_ci = gsub("[()]", "", dth_ci)
      ) %>%
  {. ->> crr_results_prep} %>%
  gt() %>%
  cols_label(
    bup_hr = "HR",
    bup_ci = "95% CI",
    mthd_hr = "HR",
    mthd_ci = "95% CI",
    of1_hr = "HR",
    of1_ci = "95% CI",
    ltc_hr = "HR",
    ltc_ci = "95% CI",
    dth_hr = "HR",
    dth_ci = "95% CI"
    ) %>%
  tab_spanner(label = "Buprenorphine initiation", columns = c(bup_hr, bup_ci)) %>%
  tab_spanner(label = "Methadone initiation", columns = c(mthd_hr, mthd_ci)) %>%
  tab_spanner(label = "Sustained remission", columns = c(of1_hr, of1_ci)) %>%
  tab_spanner(label = "Loss to clinical follow up", columns = c(ltc_hr, ltc_ci)) %>%
  tab_spanner(label = "Death", columns = c(dth_hr, dth_ci)) %>%
  opt_vertical_padding(scale = 0.25) %>%
  tab_footnote(
    footnote = "Hazard ratio",
    locations = cells_column_labels(columns = ends_with("hr"))
    ) %>%
  tab_footnote(
    footnote = "Confidence interval",
    locations = cells_column_labels(columns = ends_with("ci"))
    )
```
\newpage

## Forest plot for sHR

```{r}
#| label: fig-forest-plot

crr_results <- crr_results_prep %>%
  separate(bup_ci, c("bup_ci_lo", "bup_ci_hi"), sep = ", ", extra = "merge") %>%
  separate(mthd_ci, c("mthd_ci_lo", "mthd_ci_hi"), sep = ", ", extra = "merge") %>%
  separate(of1_ci, c("of1_ci_lo", "of1_ci_hi"), sep = ", ", extra = "merge") %>%
  separate(ltc_ci, c("ltc_ci_lo", "ltc_ci_hi"), sep = ", ", extra = "merge") %>%
  separate(dth_ci, c("dth_ci_lo", "dth_ci_hi"), sep = ", ", extra = "merge") %>%
  mutate(
    across(everything() & !Predictor, as.numeric),
    Predictor = fct_relevel(factor(Predictor),
      "Age, 5-yrs", "Male sex", "Black race", "Index year ≥2019",
      "Depression", "Anxiety", "Bipolar disorder", "Alcohol use disorder", "Cocaine use disorder",
      "Recent heavy alcohol use", "Recent cocaine use", "Recent cannabis use",
      "History of buprenorphine", "History of methadone", "No. of primary care appointments", "Use of mental health services"
      )
    )

rect_data <- data.frame(
  ymin = seq(0.5, length(crr_results$Predictor) - 0.5, by = 1),
  ymax = seq(1.5, length(crr_results$Predictor) + 0.5, by = 1),
  fill_group = factor(rep(c("odd", "even"), length.out = length(crr_results$Predictor)))
)

shr_plot_1 <- ggplot(crr_results, aes(y = fct_rev(Predictor), x = bup_hr)) +
  geom_rect(data = rect_data, aes(xmin = -Inf, xmax = Inf, ymin = ymin, ymax = ymax, fill = fill_group),
            alpha = 0.2, inherit.aes = F) +
  scale_fill_manual(values = c("odd" = "white", "even" = "#d1ced0")) +
  geom_point(shape = 15, size = 3) + # Points for HR
  geom_errorbarh(aes(xmin = bup_ci_lo, xmax = bup_ci_hi), height = 0.2) + # Horizontal error bars for CIs
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Buprenorphine initiation", y = "", x = "") +
  theme(
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    panel.background = element_rect(fill = "transparent", color = NA),
    axis.line = element_line(colour = "#6a6868"),
    axis.ticks = element_line(colour = "#6a6868"),
    legend.position = "none"
    )

shr_plot_2 <- ggplot(crr_results, aes(y = fct_rev(Predictor), x = mthd_hr)) +
  geom_rect(data = rect_data, aes(xmin = -Inf, xmax = Inf, ymin = ymin, ymax = ymax, fill = fill_group),
            alpha = 0.2, inherit.aes = F) +
  scale_fill_manual(values = c("odd" = "white", "even" = "#d1ced0")) +
  geom_point(shape = 15, size = 3) + # Points for HR
  geom_errorbarh(aes(xmin = mthd_ci_lo, xmax = mthd_ci_hi), height = 0.2) + # Horizontal error bars for CIs
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Methadone initiation", y = "", x = "") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 10),
    panel.background = element_rect(fill = "transparent", color = NA),
    axis.line.x = element_line(colour = "#6a6868"),
    axis.ticks.x = element_line(colour = "#6a6868"),
    legend.position = "none"
    )

shr_plot_3 <- ggplot(crr_results, aes(y = fct_rev(Predictor), x = of1_hr)) +
  geom_rect(data = rect_data, aes(xmin = -Inf, xmax = Inf, ymin = ymin, ymax = ymax, fill = fill_group),
            alpha = 0.2, inherit.aes = F) +
  scale_fill_manual(values = c("odd" = "white", "even" = "#d1ced0")) +
  geom_point(shape = 15, size = 3) + # Points for HR
  geom_errorbarh(aes(xmin = of1_ci_lo, xmax = of1_ci_hi), height = 0.2) + # Horizontal error bars for CIs
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Sustained remission", y = "", x = "") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 10),
    panel.background = element_rect(fill = "transparent", color = NA),
    axis.line.x = element_line(colour = "#6a6868"),
    axis.ticks.x = element_line(colour = "#6a6868"),
    legend.position = "none"
    )

shr_plot_4 <- ggplot(crr_results, aes(y = fct_rev(Predictor), x = ltc_hr)) +
  geom_rect(data = rect_data, aes(xmin = -Inf, xmax = Inf, ymin = ymin, ymax = ymax, fill = fill_group),
            alpha = 0.2, inherit.aes = F) +
  scale_fill_manual(values = c("odd" = "white", "even" = "#d1ced0")) +
  geom_point(shape = 15, size = 3) + # Points for HR
  geom_errorbarh(aes(xmin = ltc_ci_lo, xmax = ltc_ci_hi), height = 0.2) + # Horizontal error bars for CIs
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Loss to clinical follow up", y = "", x = "") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 10),
    panel.background = element_rect(fill = "transparent", color = NA),
    axis.line.x = element_line(colour = "#6a6868"),
    axis.ticks.x = element_line(colour = "#6a6868"),
    legend.position = "none"
    )

shr_plot_5 <- ggplot(crr_results, aes(y = fct_rev(Predictor), x = dth_hr)) +
  geom_rect(data = rect_data, aes(xmin = -Inf, xmax = Inf, ymin = ymin, ymax = ymax, fill = fill_group),
            alpha = 0.2, inherit.aes = F) +
  scale_fill_manual(values = c("odd" = "white", "even" = "#d1ced0")) +
  geom_point(shape = 15, size = 3) + # Points for HR
  geom_errorbarh(aes(xmin = dth_ci_lo, xmax = dth_ci_hi), height = 0.2) + # Horizontal error bars for CIs
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  labs(title = "Death", y = "", x = "") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 10),
    panel.background = element_rect(fill = "transparent", color = NA),
    axis.line.x = element_line(colour = "#6a6868"),
    axis.ticks.x = element_line(colour = "#6a6868"),
    legend.position = "none"
    )

shr_plot <- grid.arrange(shr_plot_1, shr_plot_2, shr_plot_3, shr_plot_4, shr_plot_5, ncol = 5,
             # top = textGrob("Subdistribution hazard ratios of baseline characteristics", gp = gpar(fontsize = 15)),
             left = textGrob("Baseline characteristic", rot = 90, gp = gpar(fontsize = 15)),
             bottom = textGrob("Subdistribution hazard ratio", gp = gpar(fontsize = 15)),
             widths = c(1.63, 1, 1, 1, 1))

png(filename = "my_combined_plot.png",
    width = 2800,      # Width in pixels
    height = 800,      # Height in pixels
    units = "px",      # Units for width/height (can be "in", "cm", "mm")
    res = 150)         # Resolution in pixels per inch (dots per inch)

# Draw the gtable object to the opened device
grid.draw(shr_plot)

# Close the device (CRUCIAL step to save the file)
dev.off()

cat("PNG file 'my_combined_plot.png' created.\n")

# ggsave(
#   filename = "shr_plot.png", plot = plot(shr_plot),
#   width = 20, height = 7
#   )
```
\newpage

## Secondary analysis

```{r}
#| label: fig-tte-2
#| fig-cap: Survival indexed to the first OUD diagnosis after 01-Jan-2019 in those who have not had an event in the original cohort

df_2nd <- read_excel("Data/cohort_2nd.xlsx")

# Obtain secondary survival cohort
survival_cohort_2nd <- df_2nd %>%
  mutate(time_2nd_years = time / 365.25)

cif_2nd <- tidycmprsk::cuminc(Surv(time_2nd_years, factor(event)) ~ 1,
                                    survival_cohort_2nd) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5"), linewidth = 0.8) +
  labs(
    x = "Years since index OUD diagnosis",
    y = "Cumulative incidence"
    ) +
  theme_survminer(
    font.main = c(20, "plain", "black"),
    font.submain = c(20, "plain", "black"),
    font.x = c(20, "plain", "black"),
    font.y = c(20, "plain", "black"),
    font.caption = c(20, "plain", "black"),
    font.tickslab = c(20, "plain", "black"),
    legend = c("top"),
    font.legend = c(16, "plain", "black")
    ) +
  scale_ggsurvfit(x_scales = list(limits = c(0, 5.1))) +
  theme(
    axis.line = element_line(colour = "#6a6868"),
    axis.ticks = element_line(colour = "#6a6868"),
    panel.grid.major.y = element_line(colour = "#d1ced0")
    # text = element_text(size = 24)
    ) +
  
  
  add_risktable(
    risktable_stats = "n.risk",
    stats_label = "No. at risk",
    # size = 4.2,
    size = 7,
    theme = theme_risktable_default(axis.text.y.size = 20)
    ) +
  scale_color_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  scale_fill_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  guides(color = guide_legend(nrow = 2))

cif_2nd$data <- competing_risk_df_2(
  df_in = cif_2nd$data,
  order = c("1", "2", "5", "4", "3")
  )

cif_2nd

png("cif_2nd.png", width = 800, height = 610)
cif_2nd
dev.off()

# Get 1-year, 2-year, and 5-year probabilities for buprenorphine initiation
cif_2nd_df <- (tidycmprsk::cuminc(Surv(time_2nd_years, factor(event)) ~ 1,
                          survival_cohort_2nd) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5"), linewidth = 0.8))$data %>%
  filter(outcome == "1")

cif_2nd_calc <- list()

cif_2nd_calc$year_1 <- cif_2nd_df %>%
    filter(time <= 5) %>%
    {. ->> cif_2nd_calc$year_5} %>%
    filter(time <= 2) %>%
    {. ->> cif_2nd_calc$year_2} %>%
    filter(time <= 1)

cif_2nd_calc <- list.reverse(cif_2nd_calc)

secondary_result <- list()
  
for (i in 1:length(cif_2nd_calc)) {
    
  secondary_result[[i]] <- cif_2nd_calc[[i]] %>%
    slice_max(time) %>%
    ungroup() %>%
    mutate(
      point = estimate,
      conf = paste(conf.low, conf.high, sep = ", ")
      ) %>%
    select(point, conf)
  
}

cif_report_2 <- list.cbind(secondary_result)

names(cif_report_2) <- c("1_year_point", "1_year_conf",
                         "2_year_point", "2_year_conf",
                         "5_year_point", "5_year_conf")
```
\newpage

## Hazard ratio for MOUD initiation in the secondary analysis

```{r}
#| label: tbl-model-results-2nd
#| include: false

set.seed(1110)

# Select variables to be used in the model
survival_cohort_impute_prep_2nd <- df_2nd %>%
  transmute(
    age_5yr = (age - 50) / 5, birthmale, black,
    base_dx_mental = ifelse(base_dx_anxi + base_dx_bipo + base_dx_depr >= 1, 1, 0),
    base_dx_aud, base_dx_cud,
    base_int_hazalc, base_int_cud, base_int_mud,
    base_med_bup, base_med_mthd,
    base_svc_appt, base_svc_psych, 
    below_fpl, perm_house, incarc,
    time, event = ifelse(event %in% c(1, 2), 1, 0)
    )

# Change binary variables to factor in preparation for imputation
survival_cohort_impute_prep_2nd[, -c(1, 12, 17)] <- lapply(survival_cohort_impute_prep_2nd[, -c(1, 12, 17)], as.factor)

# Impute data sets
survival_impute_prep_2nd <- replicate(
  n = K,
  rfImpute(event ~ ., survival_cohort_impute_prep_2nd),
  simplify = FALSE
  )

survival_imputed_2nd <- list()

for (i in 1:40) {

  survival_imputed_2nd[[i]] <- survival_impute_prep_2nd[[i]] %>%
    mutate_all(as.character) %>%
    mutate_all(as.numeric)

}
```

## Adjusted HR

```{r}
# Create matrix to store results
# '@ncol indicates number of outcomes
# '@nrow indiciates number of predictors
pooled_results_2nd <- matrix(, nrow = 16, ncol = 1)

# Specify the model
formula_2nd <- as.formula(
    paste("Surv(time, event) ~ ",
    paste(colnames(survival_cohort_impute_prep_2nd)[c(1:16)], collapse = " + "))
    )
  
# Fit model over all imputed data sets
fit_2nd <- lapply(survival_imputed_2nd, function(x) coxph(formula_2nd, x))
  
# Pool model results
pooled_fit_2nd <- summary(pool(fit_2nd))
  
# Point estimate and SE
point_2nd <- exp(pooled_fit_2nd$estimate)
conf.low_2nd <- exp(pooled_fit_2nd$estimate - qnorm(0.975) * pooled_fit_2nd$std.error)
conf.high_2nd <- exp(pooled_fit_2nd$estimate + qnorm(0.975) * pooled_fit_2nd$std.error)
  
# Output results
pooled_results_2nd[, 1] <- t(report_result(point_2nd, conf.low_2nd, conf.high_2nd))

# Label covariates
covariate_labels_2nd <- c(
  "Age, 5-year increments",
  "Male sex",
  "Black race",
  "Poor mental health",
  "Alcohol use disorder",
  "Cocaine use disorder",
  "Recent hazardous alcohol use",
  "Recent cocaine use",
  "Recent marijuana use",
  "History of receiving buprenorphine",
  "History of dispensing methadone",
  "No. of primary care appointments",
  "Mental health service use",
  "Below federal poverty level",
  "Permanent housing",
  "Incarcerated in past year"
)

# Output results
covariate_labels_2nd %>%
  cbind(as.data.frame(pooled_results_2nd)) %>%
  rename(Predictor = ".") %>%
  separate(V1, c("hr", "ci"), sep = " ", extra = "merge") %>%
  mutate(
    ci = gsub("[()]", "", ci),
      ) %>%
  gt() %>%
  cols_label(
    hr = "HR",
    ci = "95% CI"
    ) %>%
  opt_vertical_padding(scale = 0.25) %>%
  tab_footnote(
    footnote = "Hazard ratio",
    locations = cells_column_labels(columns = starts_with("hr"))
    ) %>%
  tab_footnote(
    footnote = "Confidence interval",
    locations = cells_column_labels(columns = starts_with("ci"))
    )
```

## Crude HRs

```{r}
#| label: tbl-model-crude-hr

crude_cov <- colnames(survival_cohort_impute_prep_2nd)[c(1:16)]

crude_hr_1 <- matrix(, nrow = 16, ncol = 2)

for (i in 1:length(crude_cov)) {
  
  crude_formula <- as.formula(
    paste("Surv(time, event) ~ ", crude_cov[i])
    )
  
  crude_fit_1 <- lapply(survival_imputed_2nd, function(x) coxph(crude_formula, x))
  
  crude_pooled <- summary(pool(crude_fit_1))
  
  crude_point <- exp(crude_pooled$estimate)
  crude_conf.low <- exp(crude_pooled$estimate - qnorm(0.975) * crude_pooled$std.error)
  crude_conf.high <- exp(crude_pooled$estimate + qnorm(0.975) * crude_pooled$std.error)
  
  crude_hr_1[i, 1] <- report_point_est(crude_point)
  crude_hr_1[i, 2] <- report_conf_int(crude_conf.low, crude_conf.high)
}

# Label covariates
covariate_labels_2nd <- c(
  "Age, 5-year increments",
  "Male sex",
  "Black race",
  "Poor mental health",
  "Alcohol use disorder",
  "Cocaine use disorder",
  "Recent hazardous alcohol use",
  "Recent cocaine use",
  "Recent marijuana use",
  "History of receiving buprenorphine",
  "History of dispensing methadone",
  "No. of primary care appointments",
  "Mental health service use",
  "Below federal poverty level",
  "Permanent housing",
  "Incarcerated in past year"
)

covariate_labels_2nd %>%
  cbind(as.data.frame(crude_hr_1)) %>%
  rename(
    Predictor = ".",
    HR = V1,
    `95% CI` = V2
    ) %>%
  gt()
```

## Crude HR 2

```{r}
#| eval: false


crude_hr_2 <- matrix(, nrow = 14, ncol = 2)

for (i in 1:(length(crude_cov) - 3)) {
  
  crude_formula <- as.formula(
    paste("Surv(time, combined_event) ~ age_5yr + birthmale + black +", crude_cov[i + 3])
    )
  
  crude_fit <- lapply(survival_imputed_2nd, function(x) coxph(crude_formula, x))
  
  crude_pooled <- summary(pool(crude_fit))[4, ]
  
  crude_point <- exp(crude_pooled$estimate)
  crude_conf.low <- exp(crude_pooled$estimate - qnorm(0.975) * crude_pooled$std.error)
  crude_conf.high <- exp(crude_pooled$estimate + qnorm(0.975) * crude_pooled$std.error)
  
  crude_hr_2[i, 1] <- report_point_est(crude_point)
  crude_hr_2[i, 2] <- report_conf_int(crude_conf.low, crude_conf.high)
}

# Label covariates
covariate_labels_2nd <- c(
  # "Age, 5-year increments",
  # "Male sex",
  # "Black race",
  "Index year 2019 or later",
  "Poor mental health",
  "Alcohol use disorder",
  "Cocaine use disorder",
  "Recent hazardous alcohol use",
  "Recent cocaine use",
  "Recent marijuana use",
  "History of receiving buprenorphine",
  "History of dispensing methadone",
  "No. of primary care appointments",
  "Mental health service use",
  "Below federal poverty level",
  "Permanent housing",
  "Incarcerated in past year"
)

covariate_labels_2nd %>%
  cbind(as.data.frame(crude_hr_2)) %>%
  rename(
    Predictor = ".",
    HR = V1,
    `95% CI` = V2
    ) %>%
  gt()
```

## Crude HR 3

```{r}
#| eval: false


crude_hr_3 <- matrix(, nrow = 15, ncol = 2)

for (i in 1:(length(crude_cov) - 2)) {
  
  crude_formula <- as.formula(
    paste("Surv(time, combined_event) ~ age_5yr + birthmale +", crude_cov[i + 2])
    )
  
  crude_fit <- lapply(survival_imputed_2nd, function(x) coxph(crude_formula, x))
  
  crude_pooled <- summary(pool(crude_fit))[3, ]
  
  crude_point <- exp(crude_pooled$estimate)
  crude_conf.low <- exp(crude_pooled$estimate - qnorm(0.975) * crude_pooled$std.error)
  crude_conf.high <- exp(crude_pooled$estimate + qnorm(0.975) * crude_pooled$std.error)
  
  crude_hr_3[i, 1] <- report_point_est(crude_point)
  crude_hr_3[i, 2] <- report_conf_int(crude_conf.low, crude_conf.high)
}

# Label covariates
covariate_labels_2nd <- c(
  # "Age, 5-year increments",
  # "Male sex",
  "Black race",
  "Poor mental health",
  "Alcohol use disorder",
  "Cocaine use disorder",
  "Recent hazardous alcohol use",
  "Recent cocaine use",
  "Recent marijuana use",
  "History of receiving buprenorphine",
  "History of dispensing methadone",
  "No. of primary care appointments",
  "Mental health service use",
  "Below federal poverty level",
  "Permanent housing",
  "Incarcerated in past year"
)

covariate_labels_2nd %>%
  cbind(as.data.frame(crude_hr_3)) %>%
  rename(
    Predictor = ".",
    HR = V1,
    `95% CI` = V2
    ) %>%
  gt()
```

## Supplementary Table 1.

```{r}
#| label: tbl-base-secondary
#| tbl-cap: Baseline characteristics for the secondary analysis

# Function for median and IQR for small samples
small_median <- function(x) median(x, na.rm = T)
small_p25 <- function(x) quantile(x, probs = 0.25, na.rm = T)
small_p75 <- function(x) quantile(x, probs = 0.75, na.rm = T)

# Display table
df_2nd %>%
  mutate(index_year_2nd = year(index_dx_date)) %>%
  # mutate(base_svc_appt = as.numeric(base_svc_appt)) %>%
  select(group, age, birthmale, black, below_fpl, perm_house, incarc, msm, idu, starts_with("base_"), index_su_mh, base_svc_psych, index_year_2nd) %>%
  tbl_summary(
    by = group,
    label = c(
      age ~ "Age", birthmale ~ "Male sex", black ~ "Black race",
      msm ~ "History of MSM", idu ~ "History of IDU",
      base_dx_depr ~ "Depression", base_dx_anxi ~ "Anxiety",
      base_dx_bipo ~ "Bipolar disorder", base_dx_schi ~ "Schizophrenia",
      base_dx_ptsd ~ "PTSD", base_dx_aud ~ "Alcohol use disorder",
      base_dx_cud ~ "Cocaine use disorder", base_int_oud ~ "Non-prescribed opioids",
      base_int_cud ~ "Cocaine", base_int_hazalc = "Unhealthy alcohol",
      base_int_mud ~ "Cannabis",
      base_med_bup ~ "Buprenorphine", base_med_mthd ~ "Methadone",
      # base_svc_use ~ "Visited primary care",
      base_svc_appt ~ "Number of visits scheduled",
      base_svc_prop ~ "Proportion of visits completed",
      base_svc_psych ~ "Mental health service use",
      index_su_mh ~ "Substance use or mental health",
      index_year_2nd ~ "Year",
      below_fpl ~ "Below federal poverty line",
      perm_house ~ "Has permanent housing",
      incarc ~ "Incarcerated in the past year"
      ),
    type = list(base_svc_appt ~ "continuous", index_year_2nd ~ "continuous"),
    value = base_int_oud ~ "1",
    statistic = list(
      # base_svc_appt ~ "{median} (p25}, {p75})",
      base_svc_prop ~ "{mean} ({sd})",
      index_year_2nd ~ "{median} ({p25}, {p75})"
      # svc_use ~ c("{N_nonmiss}", "{sum}", "{mean} ({sd})")
      ),
    digits = list(
      index_year_2nd ~ purrr::partial(style_number, digits = 0, big.mark = ""),
      base_svc_appt ~ 0,
      all_categorical() ~ c(0, 1)
      )
    ) %>%
  modify_table_body(
    mutate,
    groupname_col = case_when(
      variable %in% c("age", "birthmale", "black") ~ "Patient demographics",
      variable %in% c("below_fpl", "perm_house", "incarc") ~ "Social determinants of health",
      variable %in% c("msm", "idu") ~ "HIV acquisition factors",
      variable %in% colnames(df)[grepl("base_dx_", colnames(df))] ~ "Diagnoses",
      variable %in% colnames(df)[grepl("base_int_", colnames(df))] ~ "Recent drug use",
      variable %in% colnames(df)[grepl("base_med_", colnames(df))] ~ "History of MOUD",
      variable %in% colnames(df)[grepl("base_svc_", colnames(df))] ~ "Healthcare service utilization",
      variable %in% c("index_su_mh", "index_year_2nd") ~ "Index diagnosis"
    )
  ) %>%
  # add_overall(last = TRUE) %>%
  modify_column_indent(label, rows = row_type == "label", indent = 4L) %>%
  modify_column_indent(label, rows = row_type %in% c("level", "missing"), indent = 8L) %>%
  remove_row_type(variables = c(base_svc_appt, base_svc_prop), type = "missing") %>%
  as_gt() %>%
  opt_vertical_padding(scale = 0.25) %>%
  tab_footnote(
    footnote = "Human immunodeficiency virus",
    locations = cells_row_groups(groups = starts_with("HIV"))
    ) %>%
  tab_footnote(
    footnote = "Men who have sex with men",
    locations = cells_body(
      columns = label,
      rows = label == "History of MSM"
      )
    ) %>%
  tab_footnote(
    footnote = "Injection drug use",
    locations = cells_body(
      columns = label,
      rows = label == "History of IDU"
      )
    ) %>%
  tab_footnote(
    footnote = "Post-traumatic stress disorder",
    locations = cells_body(
      columns = label,
      rows = label == "PTSD"
      )
    )
```

## Sensitivity analysis

```{r}
#| label: fig-tte-sens

# Obtain primary survival cohort
sensitivity_cohort <- df %>%
  filter(sensitivity_cohort == 1) %>%
  mutate(
    time_years = time / 365.25,
    time_months = time / 30.417
    )

# Option to change line colors
options("ggsurvfit.switch-color-linetype" = TRUE)

# Display CIFs
cif_sensitivity <- tidycmprsk::cuminc(Surv(time_years, factor(event)) ~ 1,
                          sensitivity_cohort) %>%
  ggcuminc(outcome = c("1", "2", "3", "4", "5"), linewidth = 0.8) +
  labs(
    x = "Years since index OUD diagnosis",
    y = "Cumulative incidence"
    ) +
  theme_survminer() +
  scale_ggsurvfit(x_scales = list(limits = c(0, 5.1))) +
  theme(
    axis.line = element_line(colour = "#6a6868"),
    axis.ticks = element_line(colour = "#6a6868"),
    panel.grid.major.y = element_line(colour = "#d1ced0")
    ) +
  add_risktable(
    risktable_stats = "n.risk",
    stats_label = "No. at risk",
    size = 4.2,
    theme = theme_risktable_default(axis.text.y.size = 12)
    ) +
  scale_color_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  scale_fill_manual(
    values = c("#e27d1d", "#234e59", "#87aab8", "#00aeef", "#03afa7"),
    labels = c("Buprenorphine initiation", "Methadone initiation", "Sustained remission", "Loss to clinical follow up", "Death")
    ) +
  guides(color = guide_legend(nrow = 2))

# Import a function to create desired data frame
source("competing_risk_df_2.R")

cif_sensitivity$data <- competing_risk_df_2(
  df_in = cif_sensitivity$data,
  order = c("1", "2", "5", "4", "3")
  )

# competing_events <- cif$data %>%
#   filter(outcome == "2") %>%
#   slice_max(time) %>%
#   pull(estimate)
# 
# primary_event <- cif$data %>%
#   filter(outcome == "1") %>%
#   slice_max(time) %>%
#   pull(estimate)

cif_sensitivity
```
